Concerns:

1. Which template I use for the journal
My final Choice was: https://www.elsevier.com/__data/promis_misc/elsarticle_rinp_microarticle_template.zip
Though I need to change the images.
---
I also tried some others such as:
http://mirrors.ctan.org/macros/latex/contrib/els-cas-templates.zip

Downloaded from:
https://www.elsevier.com/authors/author-schemas/latex-instructions#crc
---

2. To show the comparision

option 1: in Introduction, I can provide the recommendation shift and in the result section I can just provide the comparison. I might have to repeat the recommendations to some extent in the results section.

Option 2: In Introduction, just mention that we have compared our findings with the shift recommendation without giving details. Then in the result section, provide both the recommendations and comparison.

For this option, though a table format seemed to be the most appropriate (to my understanding), as that will take more space, I am preferring to go for paragraphs with line boundaries (not certain to what extent this is acceptable) for each comparison. I can also just write paragrahs with no boundaries or subtitle/heading for each food group/subgroup.

3. if this become journal, people will trust the information. What I am wondering - is the research outcome that reliable? Is there any visible flaw in the methodology and conclusion? Will it be better to go through the outcome by a renal/CKD dietician also the code and outcome throughly be checked by someone other than I (just to make sure, I have done it right)? 